A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-05 manuscript.Rmd
Johnes2013 is the construction of SD3

The selected model parameters should express our expectations for the Machiavellism subscale of the short dark triad (SD3). <!-- AP: reference needed; explain the scale. What is the construct that we are measuring here? -->
As a starting point, we can use already published information.
@Jones2013 report a set of factor loadings (see Table \@ref(tab:loadings)) <!--AP what was the reference population? what was the sample size? --> and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`. <!--AP why not on the latent level? They report factor loadings after all? Please explain-->

>>>>

The selected model parameters should express our expectations for the Machiavellism subscale of the short dark triad [SD3, @Jones2013].

As a starting point, we can use already published information.
@Jones2013 report a set of factor loadings from an Exploratory Structural Equation Model [@asparouhovExploratoryStructuralEquation2009].
The estimates for the construction sample, which was recruited from Amazon’s Mechanical Turk (MTurk) and consists of 489 adults from Canada and the United States, can be seen in Table \@ref(tab:loadings))
They report a gender difference (at the manifest level) depending on the study between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.
